\begin{abstract}
% \begin{center}
% \large Enhanced Fidelity of Monte Carlo Coupled Multi-Physics Simulations for Light Water Reactors 
% \end{center}
\vspace{1cm}

This thesis presents a framework to enhance the fidelity of typical Monte Carlo (MC) coupled multi-physics simulations for Light Water Reactors (LWRs) through two key improvements. First, the introduction of multi-physics simulations with spatially continuous material properties using the Functional Expansion Tally (FET) combined with delta-tracking. Second, the incorporation of on-the-fly thermal expansion of reactor core components during MC particle tracking. The use of spatially continuous material properties is  particularly crucial to accurately modeling spatial self-shielding effects, which depend on smooth intra-fuel-pellet temperature distributions. Additionally, modeling thermal expansion is essential because the geometric data of reactor components is typically provided at room temperature, while reactors operate at much higher temperatures. Numerical experiments are conducted to assess the applicability and advantages of the proposed multi-physics framework across a range of reactor core problems, from two-dimensional pin-cell to whole-core reactor problems.

The MC multi-physics coupling with spatially continuous material properties allows for a continuous representation of intra-fuel pellet profiles, improving the accuracy of resonance absorption at the fuel-pellet periphery. This leads to a more accurate eigenvalue solution from the proposed framework. Moreover, incorporating spatially continuous material properties produces solutions that asymptotically converge to those from conventional cell-based discretized simulations with infinitesimally small cells. Similar outcomes are observed in three-dimensional pin cell and assembly problems, where the continuous representation of material properties results in more accurate solutions for both eigenvalue and axial power distributions, compared to the conventional cell-based discretization method. In typical whole-core LWR problems, the proposed method reproduces high-fidelity solutions for both eigenvalue and pin powers, while reducing simulation times by around threefold and requiring 80\% less memory than the traditional cell-based discretization using very small cells.

While the numerical results for on-the-fly thermal expansion demonstrates that the observed trends in reactivity differences due to thermal expansion for varying boron concentrations and fuel temperatures align with previous studies. Additionally, the calculated Isothermal Temperature Coefficients (ITC) show improvement when thermal expansion is considered. Using core-averaged temperatures for expansion provides fairly accurate results, but employing local temperatures can enhance accuracy further. Moreover, incorporating thermal expansion also improves solutions for depletion problems, especially at high power and high fuel burnup. These findings suggest that integrating the proposed framework into reactor modeling can significantly enhance simulation fidelity. Therefore, the framework has the potential to be incorporated into future Monte Carlo production codes to meet the growing demands for improved reactor safety.

\vfill
\end{abstract}

\clearpage