\addcontentsline{toc}{section}{Acknowledgements}
\section*{\hfill \Large Acknowledgements \hfill}
First and foremost, I am deeply grateful to Allah Almighty for His endless mercy and blessings throughout this journey. His grace has given me strength through all the challenges.

I would like to express my sincere thanks to my advisor, Prof. Deokjung Lee, for his invaluable advice, continuous encouragement, and financial support during my study in the CORE Laboratory. I am deeply grateful for the opportunity he provided me to study in his laboratory. Studying and working in the CORE Laboratory has opened new horizons of knowledge for me.

I also want to extend my appreciation to the members of my dissertation committee. Their thoughtful feedback and constructive criticism have greatly helped in refining my work and pushing me to achieve better results. My gratitude also extends to the staff at the Department of Nuclear Engineering at Ulsan National Institute of Science and Technology (UNIST).

I am also grateful to all my lab mates for their friendship, insightful discussions, and moral support. Their companionship has been a source of strength during tough times and has made the long hours in the lab much more enjoyable. 

To my beloved parents, I cannot thank you enough. Your unconditional love, support, and prayers have been my constant source of motivation. Your sacrifices and unwavering belief in me are beyond words, and I dedicate this achievement to you.

Finally, I want to thank my family, especially my dear wife. Her love, patience, and strength have been my greatest support throughout this journey. She took care of our four sons while living abroad with me during my studies, and her dedication and sacrifice have made this accomplishment possible.

I would also like to express my thanks to everyone who has supported me in any way during this journey. Your help and encouragement have meant the world to me.

During the preparation of this thesis, the author used ChatGPT-4o and ChatGPT-4 to improve readability, clarity, and conciseness of the writing. After using this tool, the author reviewed and edited the content as needed.
\clearpage